Thesis Title

### 2022-04-22 chapters/introduction.tex
Updates from Overleaf

\begin{itemize}
    \item Evaluate the current impact and applicability of metagenomics genomics in medical microbiology, both in a clinical and in surveillance and infection prevention settings; 
    \item Develop novel methods and metrics to accurately identify and estimate relative abundance of pathogens of interest through a hybrid approach of read mapping and de novo assembly methods;
    \item Standardise the process of metagenomic analysis, allowing the comparison of results obtained across domains and stakeholders
    \item Develop computational efficient and robust frameworks that allows scientists and/or medical experts with limited programming experience to rapidly and easily query the abundance of specific taxa and genes across the samples of interest, obtaining simple and intuitive reports. 
\end{itemize}

>>>>

\begin{itemize}
    \item Evaluate the current impact and applicability of metagenomics genomics in medical microbiology, both in a clinical and in surveillance and infection prevention settings; 
    \item Develop novel methods and metrics to accurately identify and estimate relative abundance of pathogens of interest through a hybrid approach of read mapping and de novo assembly methods;
    \item Standardise the process of metagenomic analysis, allowing the comparison of results obtained across domains and stakeholders
    \item Develop computationally efficient and robust frameworks that allows scientists and/or medical experts with limited programming experience to rapidly and easily query the abundance of specific taxa and genes across the samples of interest, obtaining simple and intuitive reports. 
\end{itemize}
